Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-28 1-Main.tex
sync overleaf->github
cleaning comments + remove trailing spaces

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    %numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

@@

\section{Satisfaction of Requirements}
\label{sec:requirements}
\input{7-RequirementsSatisfaction.tex}

\section{Assessment of the Modeling Solution}
\label{sec:discussion}
\input{8-Discussion.tex}

>>>>

\lstdefinelanguage{fml}{
  keywords={
    abstract,boolean,break,byte,case,catch,char,class,%
    const,continue,default,do,double,else,extends,false,final,%
    finally,float,for,goto,if,implements,import,instanceof,int,%
    interface,label,long,native,new,null,package,private,protected,%
    public,return,short,static,super,switch,this,throw,%
    throws,transient,true,try,void,volatile,while,String},%
  morekeywords={
    [3]concept,model,forEach,assert,%
  },%
  sensitive,%
  morecomment=[l]//,%
  morecomment=[s]{/*}{*/},%
  morestring=[b]",%
  morestring=[b]',%
}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\scriptsize,
    breakatwhitespace=false,
    breaklines=true,
    flexiblecolumns=true,
    captionpos=b,
    emptylines=0,
    tabsize=2
}

\lstset{style=mystyle,language=fml}

@@

\section{Satisfaction of requirements}
\label{sec:requirements}
\input{7-RequirementsSatisfaction.tex}

\section{Assessment of the modeling solution}
\label{sec:discussion}
\input{8-Discussion.tex}
